Proposal full title \\ Proposal Acronym

### 2001-10-08 drafts/IST/PartA.tex
update
svn path=/trunk/; revision=1484

@@

\\ 800 chars need some check and some other stuff:w

@@

>>>>

\usepackage{graphics}

@@

\\ 800 chars need some check and some other stuff

@@

\section*{A4 Cost Summary}
%% will look at that later
\rotatebox{90}{
\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
Participant Role(CO/P) & Participant Number & Linked to Contractor No &
Participant Short Name & Number of Person - Months & Personnel Costs &
Durable Equipment & Consumables & Travel and subsitence & Computing &
External assistance & Other Costs & Knowledge protection on Costs & 
Overhead Costs & Total Costs & Requested Contribution from the Commision &
Eligibility (Y/No)\\
}
